# Tables

(ref:tab-stationCoordinates) Stations and their associated coordinates in decimal degrees. Station names are represented by the transect abbreviation and the associated station number. The abbreviation CS denotes Cabot Strait, LL Louisbourg, HL Halifax, BBL Browns Bank, and NEC Northeast Channel.

```{r stationCoordinates, echo = FALSE, warning = FALSE, message = FALSE, results = 'asis'}
library(csasAtlPhys)
stations <- c(cabotStraitStationPolygons,
              louisbourgStationPolygons,
              halifaxStationPolygons,
              brownsBankStationPolygons,
              northeastChannelStationPolygons)
stationName <- unlist(lapply(stations, '[[', 'stationName'))
stationLon <- unlist(lapply(stations, '[[', 'longitude'))
stationLat <- unlist(lapply(stations, '[[', 'latitude'))
# order stations by number for each transect
transectName <- unlist(lapply(stations, '[[', 'transectName'))
dftemp <- data.frame(station = stationName,
                     transect = transectName,
                     longitude = stationLon,
                     latitude = stationLat)
dfs <- split(dftemp, dftemp[['transect']])
dfs <- lapply(dfs, function(k) k[order(as.numeric(gsub('\\w+\\_(\\d+)', '\\1', k[['station']]))), ])
# order transects from north to south
transectOrder <- c('cabotStrait', 'louisbourg', 'halifaxInshore', 'brownsBank', 'northeastChannel')
o <- unlist(lapply(transectOrder, function(k) which(k == names(dfs))))
dfs <- dfs[o]
df <- do.call('rbind', dfs)
table <- data.frame(Name = gsub('_', '\\\\_', df[['station']]), # have to add '\\' in front of the underscore
                    Longitude = df[['longitude']],
                    Latitude = df[['latitude']])
csasdown::csas_table(x = table,
                     caption = "(ref:tab-stationCoordinates)",
                     align = 'ccc',
                     format = 'latex')
```
(ref:tab-noClimatology) Stations, with their associated climatology period, season, and transect, that were insufficiently sampled to create a meaningful climatology. Note that the Northeast Channel stations for the 1981 to 2010 climatology period are omitted from this table as a majority of stations for both seasons were not sampled sufficiently.

```{r noClimatology, echo = FALSE, warning = FALSE, message = FALSE, results = 'asis'}
makeDirs <<- FALSE
source('../analysis/00_setupFile.R')
load(paste('../analysis', destDirData, 'newClimatologyFilled.rda', sep = '/'))
# make a data.frame of stations where a climatology couldn't be constructed
hasMissingStn <- unlist(lapply(climatology, function(k) !is.null(k[['missingStations']])))
missingStnDf <- do.call('rbind', lapply(climatology[hasMissingStn], function(k) k[['missingStations']]))
# omit northEastChannel
nec <- which(missingStnDf[['transect']] == 'northEastChannel')
missingStnDf <- missingStnDf[-nec, ]
# rename a few things to make it nice
ok <- names(missingStnDf) == 'climYear'
names(missingStnDf)[ok] <- 'climatology' 
ok <- missingStnDf[['transect']] == 'halifaxInshore'
missingStnDf[['transect']][ok] <- 'halifax'
capitalize <- function(x) {
  s <- strsplit(x, " ")[[1]]
  paste(toupper(substring(s, 1,1)), substring(s, 2),
      sep="", collapse=" ")
}
names(missingStnDf) <- sapply(names(missingStnDf), capitalize)
missingStnDf[['Transect']] <- sapply(missingStnDf[['Transect']], capitalize)
# define as factor for ordering
missingStnDf[['Transect']] <- factor(x = missingStnDf[['Transect']], levels = c('Cabot Strait', 
                                                                               'Louisbourg',
                                                                               'Halifax',
                                                                               'Browns Bank',
                                                                               'Northeast Channel')
                                                                               )
missingStnDf[['Season']] <- sapply(missingStnDf[['Season']], capitalize)
# define as factor for ordering
missingStnDf[['Season']] <- factor(x = missingStnDf[['Season']], levels = c('Spring', 'Fall'))
missingStnDf[['Station']] <- gsub('_', '\\\\_', missingStnDf[['Station']])
missingStnDf[['Climatology']] <- as.character(missingStnDf[['Climatology']])
missingStnDf <- missingStnDf[with(missingStnDf, order(Climatology, Season)), ]
rownames(missingStnDf) <- NULL
csasdown::csas_table(x = missingStnDf,
                     caption = "(ref:tab-noClimatology)",
                     align = paste(rep('c', dim(missingStnDf)[2]), collapse = ''),
                     format = 'latex')
```


(ref:tab-missionIds) The year and mission names, following the defined Bedford Institute of Oceanography convention, for the two mission defined seasons, spring and fall. No entry in a given cell indicates that a mission did not occur for that given year.

```{r missionIds, echo = FALSE, warning = FALSE, message = FALSE, results = 'asis'}
library(xtable)
library(oce)
makeDirs <<- FALSE
source('../analysis/00_setupFile.R')
load(paste('../analysis', destDirData, 'ctd.rda', sep = '/'))

fillTimeSeries <- function(x, xy){ # x is the variable, xy is the year in this case
  dxy <- diff(xy)
  if(any(dxy != 1)){
    xnew <- x
    xynew <- xy
    idx <- 1:length(xy)
    missing <- which(dxy != 1)
    for(k in 1:length(missing)){
      newidx <- missing[k] + seq(1, dxy[missing[k]] - 1, 1) / dxy[missing[k]]
      addedyear <- xy[missing[k]] + seq(1, dxy[missing[k]] - 1, 1)
      addvalue <- rep(NA, dxy[missing[k]] - 1)
      xnew <- c(xnew, addvalue)
      xynew <- c(xynew, addedyear)
      idx <- c(idx, newidx)
    }
    o <- order(idx)
    xnew <- xnew[o]
    xynew <- xynew[o]
  } else { # for those with no missing data
    xnew <- x
    xynew <- xy
  }
  return(list(x = xnew, xy = xynew))
}

startTime <- as.POSIXct(unlist(lapply(ctd, function(k) k[['startTime']])), origin = '1970-01-01', tz = 'UTC')
mission <- unlist(lapply(ctd, function(k) k[['cruiseNumber']]))
spring <- as.POSIXlt(startTime)$mon + 1 < 6
fall <- as.POSIXlt(startTime)$mon + 1 > 6
season <- vector(length = length(mission))
season[spring] <- 'spring'
season[fall] <- 'fall'
df <- data.frame(time = startTime,
                 year = as.POSIXlt(startTime)$year + 1900,
                 mission = mission,
                 season = season)
df <- df[order(df[['time']]), ]
sdf <- split(df, df[['season']])
umission <- lapply(sdf, function(k) unique(k[,names(k) %in% c('year', 'mission')]))

umission <- lapply(umission, function(k) {char <- t(apply(k, 1, as.character));
                                          df <- as.data.frame(char);
                                          names(df) <- names(k);
                                          dffill <- fillTimeSeries(x = df[['mission']], xy = as.numeric(df[['year']]));
                                          dfout <- data.frame(year = as.character(dffill$xy),
                                                              mission = dffill$x);
                                          dfout})
table <- merge(umission[[1]], umission[[2]], by = 'year', all = TRUE)
names(table)[!names(table) %in% 'year'] <- names(umission)
# replace 'NA' values with ""
table[is.na(table)] <- ""
# below is kind of fragile and not good, but fine for this
tableOrder <- unlist(lapply(c('year', 'spring', 'fall'), function(k) which(names(table) == k)))
table <- table[,tableOrder]
# capitalize names
capitalize <- function(x) {
  s <- strsplit(x, " ")[[1]]
  paste(toupper(substring(s, 1,1)), substring(s, 2),
      sep="", collapse=" ")
}
names(table) <- sapply(names(table), capitalize)

# print(xtable(table,
#       caption = 'The year and mission names, following the defined Bedford Institute of Oceanography convention, for the two mission defined seasons, spring and fall. No entry in a given cell indicates that a mission did not occur for that given year.',
#       label = 't:missionIds',
#       align = c( rep('| c ', times = dim(table)[2] + 1), '|')), # this is where xtable() gets closed
#       include.rownames = F, sanitize.colnames.function = identity,
#       sanitize.text.function = identity, hline.after = c(-1,0, dim(table)[1]),
#       caption.placement = 'top', comment = FALSE)
csasdown::csas_table(x = table,
                     caption = "(ref:tab-missionIds)",
                     align = 'cc',
                     format = "latex",
                     bold_header = FALSE # added textbf around table headers above
                     #font_size = 8
                     ) #%>%
  # add_header_above(header = addHeaderAbove,
  #                  bold = TRUE)

```
